---
title: "Chap 9: Functionals"
output: html_notebook
---

```{r, include=FALSE}
library(purrr)
```

### 9.2 My first functional: `map()`

```{r My first functional}
triple <- function(x) x * 3
map(1:3, triple)
```
#### 9.2.1 Producing atomic vectors

```{r Producing atomic vectors}
as.list(mtcars)
map_chr(mtcars, typeof)
map_lgl(mtcars, is.double)
map_int(mtcars, function(x) length(unique(x)))
map_dbl(mtcars, mean)

```
#### 9.2.2 Anonymous functions and shortcuts

```{r Anonymous functions and shortcuts}
?as_mapper()
as_mapper(~ length(unique(.x)))
map(1:3, ~ runif(2))
```
#### 9.2.3 Passing arguments with ...

You can use `pluck()` with `map()` to use a charachter vector to select elements by name, an integer vector to select by position, or a list to select by both name and position.

```{r Passing arguments with ...}
x <- list(
  list(-1, x = 1, y = c(2), z = "a"),
  list(-2, x = 4, y = c(5, 6), z = "b"),
  list(-4, x = 2, y = c(5, 6, 0))
)
map_dbl(x, "x")
map_dbl(x, 1)
map_dbl(x, list("y", 2), .default = NA) # passing arguments with ...
```

### 9.4 Map Variants

#### 9.4.1 Same type of output as input: `modify()`
```{r Same type of output as input}
df <- data.frame(
  x = 1:3,
  y = 6:4
)
map(df, ~ .x * 2)
modify(df, ~ .x * 2)
```

#### 9.4.2 Two input: `map2()` and friends

```{r Two input}
xs <- map(1:8, ~ runif(10))
xs[[1]][[1]] <- NA
ws <- map(1:8, ~ rpois(10, 5) + 1)

map2_dbl(xs, ws, weighted.mean, na.rm  =T)
```

#### 9.4.3 No outputs: `walk()` and friends

```{r No outputs, eval=FALSE}
temp <- tempfile()
dir.create(temp)

cyls <- split(mtcars, mtcars$cyl)
paths <- file.path(temp, paste0("cyl-", names(cyls), ".csv"))
walk2(cyls, paths, write.csv)

dir(temp)
```

#### 9.4.4 Iterating over values and indices: `imap()`

```{r}
imap(iris, ~ paste0("El primer valor de ", .y, " es ", .x[[1]])) # vector con nombre

x <- map(1:6, ~ sample(1000, 10))
imap_chr(x, ~ paste0("El mayor valor de la muestra ", .y, " es ", .x[[1]]))
```

### 9.5 Redue family

#### 9.5.1 Basics: `reduce()`

```{r}
l <- map(1:4, ~ sample(x = 1:10, size = 15, replace = T))
intersect(l[[1]], l[[2]])

reduce(l, intersect)

reduce(l, union)

```

#### 9.5.2 Accumulate: `acumulate()`

```{r}
accumulate(l, intersect)

accumulate(l, union)
```

### 9.6 Predicate functionals

#### 9.6.1 Basics

- `some()` / `every()`
- `detect()` / `detect_index()`
- `keep()` / `discard()`

```{r}
df <- data.frame(x = 1:3, y = c("a", "b", "c"))

some(df,  is.integer)
every(df,  is.integer)

detect(df, is.factor)
detect_index(df, is.factor)

str(keep(df, is.factor))
str(discard(df, is.factor))

```

### 9.7 Base functionals

#### 9.7.2 Mathematical concerns

```{r}
integrate(f = sin, lower = 0, 10)

str(uniroot(f = function(x) x^3, interval = c(-5, 5)))

str(optimise(f = function(x) - x^2, interval = c(-5, 5)))
plot(seq(-5, 5, length.out = 50), seq(-5, 5, length.out = 50) ^ 2, type = "l")
```




































































